---
title: "Neural Networks"
author: "Bastiaan Quast"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Neural Networks}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

An introductory sentence here.

## Backpropagation

The chapter "Neural Networks" begins with generating data for the backpropagation example.

```{r}
backpropagation_data(n=50000)
```

We can now very the objects in our Global Environment.

```{r}
ls()
```

And then run the training code.

```{r}
backpropagation_training(X, Y)
```

## Deep Learning

Next we move to deep learning, first by generating the data.

```{r}
deeplearning_data(n=50000)
```


We can now very the objects in our Global Environment.

```{r}
ls()
```

And then run the training code.

```{r, hidden_dim=4}
deeplearning_training(X, Y)
```

## Gradient Descent

Here gradient decent comes in, first we generate data.

```{r}
gradientdescent_data(n=50000)
```


We can now very the objects in our Global Environment.

```{r}
ls()
```

And then run the training code.

```{r}
gradientdescent_training(X, Y, hidden_dim=4, alpha=0.1)
```

## Recurrent Neural Networks

Finally the examples for recurrent neural networks.

```{r}
recurrentneuralnetwork_data(n=10000, binary_dim=8)
```

Check the data.

```{r}
ls()
```

Now run the training.

```{r}
recurrentneuralnetwork_training(X1, X2, Y, hidden_dim=10, alpha=0.1)
```

Return to the [overview page](EconometricsUsingR.html).
